\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
% \title{inndoor navigation}
% \author{timur.chikichev }
% \date{May 2020}

\usepackage[english]{babel}

%Includes "References" in the table of contents
\usepackage[nottoc]{tocbibind}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{float}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{dblfloatfix}
\usepackage{epstopdf}
\usepackage{diagbox}
\usepackage{csquotes}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{textgreek}
\usepackage{bbding}
\usepackage{pifont}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{color,colortbl}
\usepackage{calc}
\usepackage{stackengine}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{caption}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{graphicx}

\usepackage{blindtext}
\usepackage{enumitem}

\usepackage{lipsum}

% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Indoor Navigation Roadmap}
% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
% should not be used}
% \thanks{Identify applicable funding agency here. If none, delete this.}
% }

\author{
    \IEEEauthorblockN{
        % 1\textsuperscript{st} 
        Timur Chikichev
        \IEEEauthorblockA{
        % \textit{Skolkovo Institute of Science and Technology} \\
        \textit{Skolkovo Institute of Science and Technology}\\
        Moscow, Russia \\
        timur.chikichev@skoltech.ru}
    }
}


\maketitle

\begin{abstract}

show the evolution of IPS technology
    repeat the research of indoor positioning systems review (example, one of the most useful for now) or other IPS publicaions
    visualize IPS usage and work principles (different technologies, connections, FOMs, applications)
create financial and technical models for different IPS technologies
calculate the possible effect of merging different technologies for different applications
    calculate in FOMs / prices (novelty)
connect different technologies into single model (where possible)
create system / strategy for optimal* technology choice decision
    map / compare existing products and trends over defined figures of merit


  % Overall report / paper: no longer than 12,000 words. On average, between 8,000 - 10,000 words.
  %
  % ~ 18-25 pages of content.

  This paper reports on modern indoor positioning system (IPS) technologies.
  There are hundreds of applications for IPS technology. IPS systems are usually based on smartphones (used as a tracking device). This usage is the top interest of this paper.

% Categories and Subject Description
% C.3 [Special-purpose and application-based systems]: Realtime and embedded system
% General Terms
% Measurement, Performance, Experimentation, Design.

%/ \subsection{Keywords}
%Positioning System, Indoor positioning system, Magnetic field, Magnetic fingerprint, Systems for location determination, Wearable computing and innovative mobile devices, IPS, RTLS, GPS mobile-device-based IPS technologies

\end{abstract}

\section{Introduction}

Indoor navigation is a market solving different problems with logistics inside buildings. The problem is important because more than 90\% of time people usually spend inside the buildings\cite{Indoor_Generation}.

Time spent for logistics such as path choice, search for special places/people can't be measured, but we will agree that it's a wasted time.

Hundreds different applications, dozens of existing technologies, and no really perfect and universal solution. By word perfect we assume comparing to GPS - global, universal, precise enough for usual tasks, stable and free to people.

Existing technologies such as WiFi localization and others will be covered where possible, but the focus of paper is mostly on Indoor positioning as a product it should be: product with price, business plan, technology inside and with the need from customers.

Understanding the technology doesn't bring us to the product. There are different researches of positioning technologies\cite{Mautz2012IndoorPT, Sakpere2017ASS, Kj_fingerprinting, Brena2017}. 
%We will focus on one use case, indoor positioning system for exhibitions.
% explain the scope of paper here 

Terminology:

IPS - indoor positioning system
RTLS - reat-time location service
BLE - bluetooth low energy

\input{approach}

\input{results}

\section{Conclusions}
% 5. Conclusions & Lessons Learnt from TPR:F/TPR:A (10%)

The indoor navigation product strategy tool is in development now.
It was proven to be viable by customer discovery process and by revenue model & calculation.

However, in order use this tool efficiently, this strategy tool requires:
\begin{enumerate}
    \item to be accurate - proved to be possible but requires lot of engineering
    \item to be convenient - depends on the way of realization and would require continuous improvements
    \item the acceptance of the market segment, which shall be accurately chosen 
    \item complexity of either software or hardware
\end{enumerate}

This paper shows the usage of different modelling approaches, which allows to develop the strategy based on the product model.

Paper provides a roadmap, technology landscape and technology strategy choice that is based on the timeline and all relevant roadmap elements. 
Each statement is supported by a quantitative fact or analytics defined by the models of product and technology.

System model, created in this paper, list all important figures, components and capabilities. The key functions and system architecture are identified using common standards. Figures of merit identify capabilities and limits of technology and provide information about product development strategy. The demonstrators, patents, known products and products which can be used as a components of indoor positioning system are listed in paper and implemented into strategy.

In paper, we identify the limit for the product development performance as an average performance (root mean square trend line). This allow us to make a strategy choice, to develop a product/technology or to buy it. 

The financial valuation was developed, based on product model and sales models.
We use probabilistic models to develop strategy under uncertainty. Different scenarios (pessimistic, baseline, optimistic) are defined. 

% \section{References}


% \cite{Kj_fingerprinting, Ashraf_deepnn, Li_geomagnetic, Mautz2012IndoorPT}
% \cite{BLE_loc, microsoft}

\bibliographystyle{ieeetr}
% \bibliographystyle{unsrt}
\bibliography{literature}



\end{document}
